\chapter{Basic properties of Integers}

\section{Divisibility and primality}

\bt{``$a$ divides $b$''}, i.e., $\left(\frac{b}{a}\right)$, means \bt{$b$} is reached by \bt{$a$}, when \underline{\bt{$a$} is multiplied by \textbf{some integer}.}

\begin{Def}[Division]

    Let $a,b,x\in\mathbb{Z}$: $\left(\frac{b}{a}\right)$ means ``$b=ax$''.\\

    \noindent
    \underline{\textbf{Denoted:} $a|b$,}\\
    $\qquad$ read ``$a$ divides $b$,'' and ``$a$ doesn't divide $b$'' is, $a\nmid b$.\\
    \noindent
\end{Def}

\noindent
\textbf{Examples:}
\begin{itemize}
    \item $3\mid 6$ because $6=3\cdot2$.
    \item $3\nmid5$ because $5\neq3\cdot x$ for any $x\in\mathbb{Z}$.
    \item $2\mid 0$ because $0=2\cdot0$.
    \item $0\nmid2$ because $2\neq0\cdot x$ for any $x\in\mathbb{Z}$.
\end{itemize}


\begin{Note}
    \textbf{Note:} $a,b,x\in\mathbb{Z}$ for, ``$\left(\frac{b}{a}\right)$'' or ``$b = ax$'' are labeled, $a$: \bt{divisor}, $b$: \bt{dividend}, $x$: \bt{quotient}.
\end{Note}

\begin{Tip}
    Many problems will involve manipulating this ``$b=ax$'' equation. Whether
    it's substituting $b$ for $ax$ or vice-versa, or adding/subtracting/multiplying/dividing ``$b=ax$''
    to itself to reveal some property.\\

    \noindent
    Many definitions and theorems will relate to each other or build off one another.
    It's crucial to understand what concepts mean rather than memorizing them. This means
    the ability to derive theorems or definitions from scratch, based on intuitive
    understanding of the content.
\end{Tip}

\newpage

\noindent
Observe the following:
\begin{theo}[Properties of Divisibility]

    \textbf{Theorem 1.1.} For all $a, b, c \in \mathbb{Z}$:

    \begin{itemize}
        \item[(i)] ``$a \mid a$'', ``$1 \mid a$'', and ``$a \mid 0$''
        \item[(ii)] ``$0 \mid a$'' $\Longleftrightarrow$ ``$a = 0$''
        \item[(iii)] ``$a \mid b$'' $\Longleftrightarrow$ ``$-a \mid b$'' $\Longleftrightarrow$ ``$a \mid -b$''
        \item[(iv)] ``$a \mid b$'' $\land$ ``$a \mid c$'' $\Longrightarrow$ ``$a \mid (b + c)$''
        \item[(v)] ``$a \mid b$'' $\land$ ``$b \mid c$'' $\Longrightarrow$ ``$a \mid c$''
    \end{itemize}
\end{theo}

\noindent
Try to prove these properties before reading the proof below.
\noindent
\begin{Proof}[Properties of Divisibility]
    \textit{\textbf{Proof.}} For all $a, b, x,y \in \mathbb{Z}$:
    \begin{itemize}
        \item[(i)]  \begin {itemize}
        \item ``$a\mid a$'' means ``$a = ax$'', choosing $x = 1$ always satisfies.
        \item ``$1\mid a$'' because $a = 1\cdot a$
        \item ``$a\mid 0$'' because $0 = a\cdot 0$
    \end{itemize}
    \item[(ii)] \begin {itemize}
    \item If ``$0\mid a$'' then ``$a = 0\cdot x$'', 0 times any integer is 0, so $a = 0$
    \item If ``$a = 0$'' then ``$0 = 0\cdot x$'', $x$ can be any integer.
    \end {itemize}

    \noindent
    \item[(iii)]
    Proving $a\mid b \Longleftrightarrow -a\mid b$:
    \begin{itemize}
        \item If ``$a\mid b$'' then ``$b = ax = (-a)(-x)$'', $-x$ is some integer, say $x'$.\\
              So ``$b = (-a)x'$'' then ``$-a\mid b$''
        \item If ``$-a\mid b$'' then ``$b = (-a)x$'', choose $x$ to be some negative integer.\\
    \end{itemize}
    \vspace{-1em}
    Proving $-a\mid b \Longleftrightarrow a\mid -b$:
    \begin{itemize}
        \item If ``$-a\mid b$'' then ``$b = (-a)x$'', choose $x$ positive integer.
        \item If ``$a\mid -b$'' then ``$-b = ax$'', choose $x$ to be some negative integer.
    \end{itemize}
    \item[(iv)] If ``$a\mid b$'' and ``$a\mid c$'' then ``$b = ax$'' and ``$c = ay$'' add both equations, ``$b+c = ax+ay$''
    factor, ``$b+c = a(x+y)$'', $(x+y)$ is some integer, so ``$a\mid (b+c)$''

    \item[(v)] If ``$a\mid b$'' and ``$b\mid c$'' then ``$b = ax$'' and ``$c = by$'' substitute $b$ in $c$, ``$c = (ax)y$''\\
    shift terms, ``$c = a(xy)$'', $(xy)$ is some integer, so ``$a\mid c$''.
    \end{itemize}

\end{Proof}

\newpage

\begin {theo}[Reflexive Divisibility]

For all $a, b \in \mathbb{Z}$: ``$a \mid b$'' $\land$ ``$b \mid a$'' $\Longleftrightarrow$ ``$a = \pm b$''. Additionally, ``$a \mid 1$'' $\Longleftrightarrow$ ``$a = \pm 1$''.
\end{theo}

\begin{Proof}[Reflexive Divisibility]
    \textit{\textbf{Proof.}} For all $a, b, x,y \in \mathbb{Z}$:\\

    \noindent
    Proving ``$a\mid b$'' $\land$ ``$b\mid a$'' $\Longrightarrow$ ``$a = \pm b$'':
    \begin{align*}
        a\mid b \quad a\mid b \quad \quad & \textit{ Given}                      \\
        b = ax \quad a = by         \quad & \textit{ Definition of Division}     \\
        ab = (ax) (by)              \quad & \textit{ Multiplying both equations} \\
        ab = (ab)(xy)               \quad & \textit{ Shift terms}                \\
        1 = xy                      \quad & \textit{ Divide both sides by } ab
    \end{align*}

    \noindent
    $x$ and $y$ are integers, so ``$x = y = 1$''. Substitute $x$ and $y$,
    \hspace{-3em}
    \begin{align*}
        b = a(1) \quad a = b(1) \quad & \textit{ Substitute}              \\
        a = b \quad                   & \textit{ Simplify } \hspace*{9em}
    \end{align*}
    $x$ or $y$ could be $\pm$, so ``$a = \pm b$''. Now ``$a=\pm b$'' $\Longrightarrow$ ``$a\mid b$'' and ``$b\mid a$''.
    From Theorem 1.1, we can use (i) to show ``$a\mid a$'' substitute $b$ in for $a$, ``$a\mid b$'' or $b\mid a$.\\

    \noindent
    Proving ``$a\mid 1$'' $\Longrightarrow$ ``$a = \pm 1$'':
    \begin{align*}
        a\mid 1 \quad \quad  & \textit{ Given}                  \\
        1 = ax \quad \quad   & \textit{ Definition of Division} \\
        1 = a(1) \quad \quad & \textit{ Simplify}               \\
    \end{align*}
    $a$ must be 1, $x$ could be $\pm$, so ``$a = \pm 1$'' then ``$a\mid \pm 1$'' so ``$a\mid 1$''.
\end{Proof}

\begin{Def}[Cancellation Law]

    Let $a,b,c\in\mathbb{Z}$: If ``$ab=ac$'' and ``$a\neq 0$'' then ``$b=c$''.

\end{Def}

\noindent
I.e., given ``$b=c$'' multiplying both sides by $a$ yields ``$ab=ac$'', and still $b=c$.

\newpage

\begin{Def}[Prime Numbers]

    $p\in\mathbb{Z}$ is prime if $p\neq 0$ and $p$ has no divisors other than $1$ and $p$.
\end{Def}
\underline{We will \textbf{only consider positive prime numbers},} in this text. Examples of primes are:
$$2,3,5,7,11,13,17,\dots$$

\begin{Def}[Composite Numbers]

    $n,a,b\in\mathbb{Z}$ is composite if $n=ab$ and $1<a<n$ and $1<b<n$.
\end{Def}
I.e., a composite number is a number can be factor into two integers, other than $1$ and itself.

\noindent
\textbf{Examples:}
\begin{itemize}
    \item $4$ is composite because $4=2\cdot2$.
    \item $6$ is composite because $6=2\cdot3$.
\end{itemize}

\noindent
Briefly observe the following:
\begin{theo}[Division Algorithm]

    For all $a,b\in\mathbb{Z}$, $b\neq0$, there exists unique $q,r\in\mathbb{Z}$ such that $a=bq+r$ and $0\leq r<|b|$.
\end{theo}

\noindent
To dissect, for all $a,b,q,r\in\mathbb{Z}$, $b\neq0$, $q$ and $r$ exist uniquely such that:

\begin{center}
    \HUGE{``\textcolor{red}{$a$}=\textcolor{OliveGreen}{$b$}\textcolor{orange}{$q$}+\textcolor{blue}{$r$}''}\\
    \vspace*{.5em}
    \LARGE{\textcolor{red}{\textbf{Dividend}} = \textcolor{OliveGreen}{\textbf{Divisor}} $\cdot$ \textcolor{orange}{\textbf{Quotient}} + \textcolor{blue}{\textbf{Remainder}}}\\
    \Large{\textcolor{OliveGreen}{$b$} fits into \textcolor{red}{$a$} \textcolor{orange}{$q$} times with \textcolor{blue}{$r$} left over.}
\end{center}

\noindent
\textbf{Examples:}
\begin{itemize}
    \item $8=4\cdot2+0$
    \item $5=3\cdot1+2$
\end{itemize}

\begin{Note}
    \textbf{Note:} Theorem 1.3 is called the Division Algorithm, despite not being an algorithm.
\end{Note}

\newpage

\begin{Proof} [Division Algorithm]
    \textit{\textbf{Proof.}} For all $a,b\in\mathbb{Z}$, $b\neq0$, there exists unique $q,r\in\mathbb{Z}$ such that $a=bq+r$ and $0\leq r<|b|$.\\

    \noindent
    The definition of division ``$b\mid a$'' then ``$a=bx$'', $x\in\mathbb{Z}$. Subtract $bx$ from both sides, ``$a-bx=0$'', working out evenly to 0.
    Freeze $a$ and $b$, and vary $x$ yields a set of outputs, $S$:
    \large{$$S=\{a-bx:x\in\mathbb{Z}\}$$}
    \normalsize
    \begin{center}
        $a$ fits into $b$, for some $x$ times. E.g., ``$b=2$, $a=6$'':
    \end{center}
    \begin{center}
        \begin{tabular}{c|cc}
            $x$ & $a-bx$                \\
            \hline
            0   & 0      & $=6-2\cdot0$ \\
            1   & 4      & $=6-2\cdot1$ \\
            2   & 2      & $=6-2\cdot2$ \\
            3   & 0      & $=6-2\cdot3$ \\
            \hline
            4   & -2     & $=6-2\cdot4$ \\
        \end{tabular}
    \end{center}

    \noindent
    Let r be outputs of $S$ and ``$q:=x$'' then ``$a-bq=r$'' add $bx$ to both sides, \underline{``$a=bq+r$''}\\

    \noindent
    \textbf{Intuitively:} I cut a cake of size $a$ into pieces of $b$ width for $q$ people. Leftovers $r$
    can't be more than the size of my cake: I either have none left or shared nothing, i.e., \underline{``$0\leq r<b$''}\\

    \noindent
    We found our lower bound: \Large{$S=\{a-bx:x\in\mathbb{Z}, a-bx\geq0\}$.}\\

    \normalsize
    \noindent
    \textbf{Formally:} By the Well-Ordering Principle, there exists a smallest element in $S$, call it $r$.
    To show existence in $S$, choose ``$x=0$'' then ``$a-b(0)=a$'' we are left with ``$a\geq 0$''\\

    \noindent
    Without loss of generality, assume ``$a<0$''. To satisfy ``$a-bx\geq0$'' choose ``$x=a$'' yielding
    ``$a-ba=a(1-b)$'' we know ``($a<0)$'' and ``($b\geq1$)'' as ``$0\leq r <b$''. So ``$(1-b)\leq0$''. Hence
    ``$a(1-b)\geq0$'' as ``$(n<0\,\cdot m\leq0)=p\geq0$'' for some $n,m,p\in\mathbb{Z}$. So \underline{$S$ is not empty.}\\

    \noindent
    To show \underline{``$r<b$''} we argue by contradiction ``$r\geq b$'' then ``$r=a-bq\geq b$'' subtract $b$ from both sides,
    ``$(r-b=a-bq-b)\geq (b-b$ = 0)'' factoring we see ``$r-b=a-b(q+1)$'' since
    $q+1$ is some integer say $q'$, ``$r-b=a-bq'$'' showing \underline{``$(r-b)<r$'' contradicting our assumption.}\\

        \noindent
        To show $q$ and $r$ are unique, we argue by contradiction, assume there exists another pair $q',r'$
        such that ``$a=(bq'+r')=(bq+r)$'' and ``$0\leq r'<b$''. Without loss of generality, assume ``$r'\geq r$''
        re-arrange both sides, ``$r'-r=bq-bq'$'' factor ``$r'-r=b(q-q')$'', then ``$b\mid r'-r$''
        , but ``$0\leq r'-r<b$'' so ``$r'-r=0$' therefore ``$r'=r$'' showing \underline{``$r$ is unique''}.
        ``$b(q-q')=0$'' therefore ``$(q-q')=0$'' hence ``$q=q'$'' showing \underline{``$q$ is unique''}.
\end{Proof}


