\section{Computers \& Number Base Systems}
    \noindent 
   The following section introduces the foundation of all computer science.
 

\begin{Def}[Turing Machine]

    A \textbf{Turing Machine} is a theoretical computational model used to describe the capabilities of a general-purpose \textbf{computer}. It consists of an infinite tape (memory) and a read/write head processing symbols on the tape, one at a time, according to a set of predefined rules. The machine moves left or right, reading or writing symbols, and changing states based on what it reads. 
    
    The machine \textbf{halts} once it reaches a final state or continues indefinitely. Serving as a flexible, \textbf{higher-order function} (a function which receives functions).
\end{Def}

\begin{Def}[Von Neumann Architecture]

    Modern computers operate on a model known as the \textbf{Von Neumann architecture}, which consists of three primary components:
    \begin{enumerate}
        \item \textbf{Memory}: Stores data and instructions as sequences of bits.
        \item \textbf{Arithmetic and Logic Unit (ALU)}: Executes operations such as addition, subtraction, multiplication, and division on numbers stored in memory.
        \item \textbf{Control Unit}: Directs the execution of instructions and manages the flow of data between memory and the ALU.
    \end{enumerate}
    
    Where numbers are stored in memory cells, each cell holding an integer value represented in a fixed base, typically \(B = 2\), meaning \textbf{binary}. Where each digit is less than the base \(B\). We represent integers in memory as:
    
    \[
    a = \sum_{i=0}^{k-1} a_i B^i
    \]
    
    where \( a_i \) represents the individual digits, and \(B\) is the base. For large integers, computations may require manipulating several memory cells to store the full number.
\end{Def}

\begin{Tip}
    \textbf{Alan Turing} (1912-1954) was a British mathematician and logician. In 1936, he introduced the concept of the Turing machine, laying the groundwork for theory of computation. During World War II Turing broke the German Enigma encrypted code shifting the tides of the war. He after worked on early computers and artificial intelligence, proposing the ``Turing Test'', defining machine intelligence. Tragically, Turing's life was cut short by personal and professional persecution against his homosexuality, dying at 41.
\end{Tip}

\newpage

\begin{Tip}
    John von Neumann (1903-1957) was a Hungarian-American mathematician and polymath who made fundamental contributing to, mathematics, physics, economics, and computer science. He is best known for developing the ``\textit{Von Neumann Architecture.}''
\end{Tip}

\noindent
\textbf{Example:} Consider the integer $a = 13$, and let us represent it in base $B = 2$ (binary). We can express this number as a sum of powers of $2$, corresponding to the binary representation of $13$:
    
\[
a = 1 \cdot 2^3 + 1 \cdot 2^2 + 0 \cdot 2^1 + 1 \cdot 2^0 = 8 + 4 + 0 + 1 = 13
\]

\noindent
In binary, this is represented as the sequence of digits: $a = (1101)_2$. Here, the coefficients $a_3 = 1$, $a_2 = 1$, $a_1 = 0$, and $a_0 = 1$ correspond to the binary digits of $13$.

\noindent
Similarly, if we want to represent $a = 45$ in base \textbf{$B = 10$ (decimal)}, we write:

\[
a = 4 \cdot 10^1 + 5 \cdot 10^0 = 40 + 5 = 45
\]

\noindent
In this case, the coefficients $a_1 = 4$ and $a_0 = 5$ correspond to the decimal digits of $45$.


\begin{Def}[Hexadecimal]
    
        \textbf{Hexadecimal} base $B=16$, using digits $0-9$ and the letters $A-F$, where $A=10$, $B=11$, $C=12$, $D=13$, $E=14$, and $F=15$. Hexadecimal is commonly used in computing due to its compact representation of binary data. For example, a \textbf{byte} (8 bits) can be represented as two hexadecimal digits, simplifying the display of binary data.
\end{Def}


\begin{theo}[Base $2\leftrightarrow16$ Conversion]

    Let bases \( B:=2 \) (binary) and \( H:=16 \) (hexadecimal). At a high-level:

    \vspace{.5em}
    
    \noindent \textbf{Binary to Hexadecimal:}
    \begin{enumerate}
        \item Group $B$ digits in sets of 4, right to left. \textbf{Pad} leftmost group with 0's if necessary for a full group.
        \item Compute each group, replacing the result with their $H$ digit.
        \item Finally, combine each $H$ group.
    \end{enumerate}
    
    \noindent \textbf{Hexadecimal to Binary:}
    \begin{enumerate}
        \item Convert each $H$ digit into a 4 bit $B$ group.
        \item Finally, combine all $B$ groups.
    \end{enumerate}
    \noindent
    Additionally we may also trim any leading 0's.
\end{theo}

\newpage

\noindent
\textbf{Example:}
    \begin{itemize}
        \item Binary to Hexadecimal:
        \[
        101101111010_2 \quad \Rightarrow \quad \text{Group as } ([1011] \ [0111] \ [1010]) \quad \Rightarrow \quad B7A_{16}
        \]
        \item Hexadecimal to Binary:
        \[
        3F5_{16} \quad \Rightarrow \quad [0011]\ [1111]\ [0101]_2 \Rightarrow \quad 1111110101_2
        \]
        \noindent
    \end{itemize}
    \noindent
The following definition is for completeness: applications of such a base are currently uncommon.
\begin{Def}[Unary]
    
    \textbf{Unary}, base $B=1$. A system where each number is represented by a sequence of $B$ symbols. Where the number $n$ is represented by $n$ symbols. Often used in theoretical computer science to prove the existence of computable functions.
\end{Def}
\noindent
\textbf{Example:} The number $5$ in unary is represented by $5$ symbols: $5 = \texttt{IIIII}$ or $2= \texttt{II}$. There is no concept of 0, the absence of symbols represents 0.\\
\begin{Def}[Most \& Least Significant Bit]
    
    In a binary number, the \textbf{most significant bit (MSB)} is the leftmost bit. The \textbf{least significant bit (LSB)} is the rightmost bit.
\end{Def}

\begin{theo}[Adding Binary]

    We may use the add and carry method alike decimal addition:
    \textbf{Binary Addition Rules:}
    \begin{itemize}
        \item $0 + 0 = 0$
        \item $0 + 1 = 1$
        \item $1 + 0 = 1$
        \item $1 + 1 = 0 \quad (\text{add 1 to the next digit (left)})$
    \end{itemize}
    \noindent
    We call the last step, \textbf{carry}, as we carry our overflow to the next digit.
\end{theo}
    \newpage

    \noindent
    \textbf{Example:} Adding $0010\ 0011\ 0100_2$ and $0100_2$:
    \[
    \begin{array}{r}
    0010\ 0011\ 0100 \\
    + \quad\quad\ \ \ 0100 \\
    \hline
    0010\ 0011\ 1000
    \end{array}
    \]
\noindent
Where the $0100+0100=1000$ as we carry the an overflow of 1. 

\begin{theo}[Signed Binary Numbers - Two's Complement]
    
    In a \textbf{two's complement system}, an $n$-bit signed (positive or negative) binary number can represent values in the range $[-2^{n-1}, 2^{n-1}-1]$. Then by most significant bit (MSB):
    \begin{itemize}
        \item If MSB is 0, the number is positive;
        \item If MSB is 1, the number is negative.
    \end{itemize}
    \noindent
    \textbf{Conversion to Two's Complement :}
    \begin{enumerate}
        \item Take an unsigned binary number and invert all bits, turning 0's to 1's and 1's to 0's.
        \item Finally add 1 to the least significant bit.
    \end{enumerate}
\end{theo}
\textbf{Example:} Converting $-5$ into a 4-bit two's complement:
    \begin{align*}
        5 \rightarrow 0101 \quad & \text{(binary for 5)} \\
         1010 \quad & \text{(inverted)} \\
         1011 \quad & \text{(add 1)}
    \end{align*}
    Thus, $-5$ is represented as $1011$ in 4-bits under two's complement.
